---
title: "Bachelor pre-process"
author: "Caroline Hommel"
date: "10/24/2022"
output: html_document
---

```{r}
pacman::p_load(readbulk, tidyverse, ggplot2, ggpubr, cluster, factoextra, PerformanceAnalytics, lme4, tibble, vctrs)
```

```{r}
fixIt <- read_bulk('forfatterGen_data/rigtig data') 
#fixIt <- read_bulk('forfatterGen_data/vores filer') 

#deleting id's on those not fit for the experiment
# omit <- c("mbazte","3asjq1","3spth5","ck3gqh", "3asjq1", "8mmtx9", "bcrg2j",
# '3ovwc1','2onc8w','7dykwl', "zdf9td", "yxw221", "wvg4cm", "vfsse3", "uwy36q", "rez8hg", "gyk81z", "9czh3l", "4t0bm6", "10cshl", "youp6n")
# fixIt <- filter(fixIt, !(exp_id %in% omit))

```

Fixing the data frame
```{r}
#Removing kolonner vi ikke skal bruge 
fixIt2 <- fixIt %>% 
  select(rt, stimulus, response, exp_id, uddannelse, dysleksi, foerstesprog, books, age, gender)

#Seperates the response column into new rows by ,
fixIt2 <- separate_rows(fixIt2, response, sep = ",")

#Creates new columns, one with the question, one with the answer
fixIt2 <- fixIt2 %>%
        mutate(valgmulighed = str_remove_all(response, ":.*|\\..*")) %>% 
        mutate(Svar = str_remove_all(response, ".*:|\\..*"))
```

Fixing syntax strings
```{r}
#remove weird syntax from strings
fixIt2 <- fixIt2 %>%
  mutate(gender = str_remove_all(gender, "[}]")) %>% 
  mutate(gender = str_remove_all(gender, ".*:|\\..*")) %>%  
  mutate(uddannelse = str_remove_all(uddannelse, ".*:|\\..*")) %>% 
  mutate(uddannelse = str_remove_all(uddannelse, "[}]")) %>% 
  mutate(dysleksi = str_remove_all(dysleksi, ".*:|\\..*")) %>% 
  mutate(dysleksi = str_remove_all(dysleksi, "[}]")) %>% 
  mutate(foerstesprog = str_remove_all(foerstesprog, ".*:|\\..*")) %>% 
  mutate(foerstesprog = str_remove_all(foerstesprog, "[}]")) %>% 
  mutate(books = str_remove_all(books, ".*:|\\..*")) %>% 
  mutate(books = str_remove_all(books, "[}]")) %>% 
  mutate(age = str_remove_all(age, ".*:|\\..*")) %>% 
  mutate(age = str_remove_all(age, "[}]")) %>% 
  mutate(valgmulighed = str_remove_all(valgmulighed, "[{]")) %>% 
  mutate(Svar = str_remove_all(Svar, "[}]")) %>% 
  mutate(response = str_remove_all(response, "[{]")) %>% 
  mutate(response = str_remove_all(response, "[}]"))

fixIt2 <- as.data.frame(sapply(fixIt2, function(x) gsub("\"", "", x)))

#removing rows 
fixIt2 <- fixIt2 %>% 
  filter(!grepl('<p>', stimulus)) %>% 
  filter(!grepl('ordblind', response)) %>% 
  filter(!grepl('fakultet', response)) %>% 
  filter(!grepl('Køn', response)) %>% 
  filter(!grepl('Q0', response)) %>% 
  filter(!grepl('førstesprog', response))

fixIt2 <- fixIt2 %>% drop_na()
```

Audio, forfatter, Ordforråd 
```{r}
fixIt2['accuracy'] <- NA

fixIt2$accuracy <- ifelse(fixIt2$Svar == "gis"|fixIt2$Svar == "charlatan"|fixIt2$Svar == "dorsk"|fixIt2$Svar == "resolut"|fixIt2$Svar == "reptil"|fixIt2$Svar == "relikvie"|fixIt2$Svar == "sololie"|fixIt2$Svar == "reservat"|fixIt2$Svar == "istap"|fixIt2$Svar == "trubadur"|fixIt2$Svar == "radering"|fixIt2$Svar == "fjante"|fixIt2$Svar == "kattun"|fixIt2$Svar == "halsstarrig"|fixIt2$Svar == "grif"|fixIt2$Svar == "dadle"|fixIt2$Svar == "idelig"|fixIt2$Svar == "rudel"|fixIt2$Svar == "sufflør"|fixIt2$Svar == "prelle"|fixIt2$Svar == "krill"|fixIt2$Svar == "spagat"|fixIt2$Svar == "knibsk"|fixIt2$Svar == "chalup"|fixIt2$Svar == "svanger"|fixIt2$Svar == "dirk"|fixIt2$Svar == "puld"|fixIt2$Svar == "rulam"|fixIt2$Svar == "trappist"|fixIt2$Svar == "spæge"|fixIt2$Svar == "chihuahua"|fixIt2$Svar == "anløben"|fixIt2$Svar == "skæfte"|fixIt2$Svar == "klandestin",  1, ifelse(fixIt2$stimulus == "audio/forf/Centrifuge.mp3" & fixIt2$response == 1 
|fixIt2$stimulus == "audio/forf/Krank.mp3" & fixIt2$response == 3 
|fixIt2$stimulus == "audio/forf/Gobelin.mp3" & fixIt2$response == 1
|fixIt2$stimulus == "audio/forf/Asiet.mp3" & fixIt2$response == 2
|fixIt2$stimulus == "audio/forf/Daggert.mp3" & fixIt2$response == 2
|fixIt2$stimulus == "audio/forf/Longjohn.mp3" & fixIt2$response == 3
|fixIt2$stimulus == "audio/forf/Chatol.mp3" & fixIt2$response == 2
|fixIt2$stimulus == "audio/forf/Albatros.mp3" & fixIt2$response == 1
|fixIt2$stimulus == "audio/forf/Fontaene.mp3" & fixIt2$response == 3
|fixIt2$stimulus == "audio/forf/Voliere.mp3" & fixIt2$response == 0
|fixIt2$stimulus == "audio/forf/Unbraconogle.mp3" & fixIt2$response == 1
|fixIt2$stimulus == "audio/forf/Terrin.mp3" & fixIt2$response == 2
|fixIt2$stimulus == "audio/forf/Metronom.mp3" & fixIt2$response == 1
|fixIt2$stimulus == "audio/forf/Gejstlig.mp3" & fixIt2$response == 2
|fixIt2$stimulus == "audio/forf/Alkymi.mp3" & fixIt2$response == 1
|fixIt2$stimulus == "audio/forf/Mokkasin.mp3" & fixIt2$response == 0
|fixIt2$stimulus == "audio/forf/Eufori.mp3" & fixIt2$response == 1
|fixIt2$stimulus == "audio/forf/Litografi.mp3" & fixIt2$response == 3
|fixIt2$stimulus == "audio/forf/Cisterne.mp3" & fixIt2$response == 1 
|fixIt2$stimulus == "audio/forf/Gadekaer.mp3" & fixIt2$response == 0 
|fixIt2$stimulus == "audio/forf/Lazaret.mp3" & fixIt2$response == 1 
|fixIt2$stimulus == "audio/forf/Obelisk.mp3" & fixIt2$response == 1 
|fixIt2$stimulus == "audio/forf/Visir.mp3" & fixIt2$response == 1 
|fixIt2$stimulus == "audio/forf/Trawler.mp3" & fixIt2$response == 1 
|fixIt2$stimulus == "audio/forf/Pergola.mp3" & fixIt2$response == 2 
|fixIt2$stimulus == "audio/forf/Pendel.mp3" & fixIt2$response == 3 
|fixIt2$stimulus == "audio/forf/Vimpel.mp3" & fixIt2$response == 2 
|fixIt2$stimulus == "audio/forf/Polio.mp3" & fixIt2$response == 3 
|fixIt2$stimulus == "audio/forf/Lumbago.mp3" & fixIt2$response == 2 
|fixIt2$stimulus == "audio/forf/Likvid.mp3" & fixIt2$response == 3 
|fixIt2$stimulus == "audio/forf/Stramaj.mp3" & fixIt2$response == 0 
|fixIt2$stimulus == "audio/forf/Skurv.mp3" & fixIt2$response == 0, 1, ifelse(fixIt2$Svar == "Ikke forfatter", 0, ifelse(fixIt2$valgmulighed == "Forfatter3" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter5" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter7" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter10" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter12" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter13" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter16" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter18" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter21" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter22" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter24" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter25" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter26" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter28" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter30" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter32" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter35" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter36" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter38" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter40" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter44" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter46" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter47" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter50" & fixIt2$Svar == "Forfatter"|
fixIt2$valgmulighed == "Forfatter52" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter53" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter54" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter55" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter58" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter60" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter62" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter65" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter67" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter69" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter71" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter72" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter74" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter75" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter77" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter80" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter82" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter84" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter87" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter89" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter91" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter93" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter95" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter96" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter98" & fixIt2$Svar == "Forfatter" |
fixIt2$valgmulighed == "Forfatter100" & fixIt2$Svar == "Forfatter", 1, 
ifelse(fixIt2$valgmulighed == "Forfatter1" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter2" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter4" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter6" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter8" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter9" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter11" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter14" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter15" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter17" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter19" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter20" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter23" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter27" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter29" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter31" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter34" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter33" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter37" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter39" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter42" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter43" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter41" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter45" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter48" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter49" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter51" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter56" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter57" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter59" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter61" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter63" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter64" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter66" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter68" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter70" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter73" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter76" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter78" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter79" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter81" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter83" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter85" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter86" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter88" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter90" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter92" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter94" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter97" & fixIt2$Svar == "Forfatter"|fixIt2$valgmulighed == "Forfatter99" & fixIt2$Svar == "Forfatter", -1, 0)))))
```

Data-sæt til arbejde
```{r}
Work <- fixIt2 %>% 
  select(rt, exp_id, uddannelse, dysleksi, foerstesprog, books, age, gender, valgmulighed, Svar, accuracy)
```

Splitter til tre data frames
```{r}
Work_numbers = Work %>% 
                filter(valgmulighed %in% c(0,1,2,3))

Work_Ordfor = Work %>% 
              mutate(ordfor = paste0(str_count(valgmulighed, "Ordforråd"))) %>%
              filter(ordfor == 1)

Work_Forfatter = Work %>% 
              mutate(Forfatter = paste0(str_count(valgmulighed, "Forfatter"))) %>%
              filter(Forfatter == 1)
```

Data frame til analyse
```{r}
#udregner sum af korrekte svar for hver test per deltager og laver dataframe
FA <- as.data.frame(aggregate(Work_Forfatter$accuracy, by=list(ID=Work_Forfatter$exp_id, Work_Forfatter$age, Work_Forfatter$books, Work_Forfatter$gender, Work_Forfatter$uddannelse), FUN=sum))
FB <- as.data.frame(aggregate(Work_Ordfor$accuracy, by=list(ID=Work_Ordfor$exp_id), FUN=sum))
FC <- as.data.frame(aggregate(Work_numbers$accuracy, by=list(ID=Work_numbers$exp_id), FUN=sum))

Final <- merge(FA, FB, by = 'ID')
Final <- merge(Final, FC, by = 'ID')

#rename columns
names(Final)[2] <- "Alder"
names(Final)[3] <- "Bøger"
names(Final)[4] <- "Køn"
names(Final)[5] <- "Fakultet"
names(Final)[6] <- "Forfatter"
names(Final)[7] <- "Ord"
names(Final)[8] <- "LydOrd"

Final$total_ord <- Final$LydOrd+Final$Ord
Final$acc_forf_percent <- Final$Forfatter/50*100
Final$acc_voc_percent <- Final$total_ord/66*100

```

```{r}
ggplot(Final, aes(x = acc_voc_percent, y = acc_forf_percent, fill=acc_voc_percent)) + 
  geom_bar(stat = 'identity', position = 'dodge') +
  facet_wrap(~Fakultet) 
```

```{r}
plot(acc_voc_percent ~ acc_forf_percent, Final, col=Final$total_ord)

Final$color <- ifelse(Final$Fakultet == "Humanistisk", "#E7298A", ifelse(Final$Fakultet == "Naturvidenskabeligt", "green", ifelse(Final$Fakultet == "Andet", "#7570B3", ifelse(Final$Fakultet == "Ingeniør", "blue", ifelse(Final$Fakultet == "Business", "#1B9E77", ifelse(Final$Fakultet == "Samfundsvidenskabeligt", "red", ifelse(Final$Fakultet == "Teknik, IT og Design", "#D95F02", "black")))))))

plot(acc_voc_percent ~ acc_forf_percent, Final,
     col = color,
     main = 'custom color scheme based on Dark2', cex = 2)
# legend(x = 'bottomright',
#        legend = as.character(Final$Fakultet),
# #        legend = unique(as.character(Final$Fakultet)),
#        col = Final$color, pch = par("pch"), bty = 'n', xjust = 1)
```

```{r}
cols <- c('green','blue');
ylim <- c(0,100);
par(lwd=6);
barplot(
    t(Final[c('acc_forf_percent','acc_voc_percent')]),
    beside=T,
    ylim=ylim,
    border=cols,
    col='white',
    names.arg=Final$ID,
    xlab='Sprint',
    ylab='Percentage correct',
    legend.text=c('Author accuracy','Vocabulary accuracy'),
    args.legend=list(text.col=cols,col=cols,border=cols,bty='n')
);
```

```{r}
#hvor ligger chance-level -find ud af, hvornår folk ikke er en robot 
plot(pbinom(1:34,34,1/3))
plot(pbinom(1:32,32,1/4))
```

FORARBEJDE TIL MODELLOS

Logtransform + roundpastecs
```{r}
# Log-transforming
Final <- Final %>% 
  mutate(log_forfatter = log(Forfatter))

Final <- Final %>% 
  mutate(log_ord = log(Ord))

Final <- Final %>% 
  mutate(log_lydord = log(LydOrd))

# Checking for normality again
#ordforråd u. lyd
round(pastecs::stat.desc(Final$Ord, basic = FALSE, norm = TRUE), digits = 2)
ggplot(Final, aes(x = Ord))+
  geom_histogram() +
  theme_minimal()
#ordforråd m. lyd
round(pastecs::stat.desc(Final$LydOrd, basic = FALSE, norm = TRUE), digits = 2)
ggplot(Final, aes(x = LydOrd))+
  geom_histogram() +
  theme_minimal()
#forfattergenkendelse
round(pastecs::stat.desc(Final$Forfatter, basic = FALSE, norm = TRUE), digits = 2)
ggplot(Final, aes(x = Forfatter))+
  geom_histogram() +
  theme_minimal()
```
Tjekker for normalitet
```{r}
#Normality -Tjek begge ordforrådstest hver for sig ift. ceiling effects
ggdensity(Final$acc_voc_percent, 
          main = "Density plot of tooth length",
          xlab = "Percent accuracy vocabulary")

ggdensity(Final$acc_forf_percent, 
          main = "Density plot of tooth length",
          xlab = "Percent accuracy authors")

ggqqplot(Final$acc_voc_percent)
ggqqplot(Final$acc_forf_percent)
ggqqplot(Final$LydOrd)
ggqqplot(Final$Ord)

shapiro.test(Final$acc_voc_percent)
shapiro.test(Final$acc_forf_percent)

hist(Final$total_ord, col='steelblue', main='Normal')

qqnorm(Final$total_ord, main='Normal')
qqline(Final$total_ord)
```

Correlation analysis
```{r}
cor.test(Final$acc_voc_percent, Final$acc_forf_percent, method = "spearman", na.action = "na.exclude")
# Runnings a Spearman's Rho which is one of the non-parametric tests to use if the variables are not normally distributed. otherwise pearson 

#find estimate and *r squared

#The conditional R^2 = 0.70, which means that 70% of the variance is explained by our model.

```
P > 0.05 so there is no significant relationship between vocabulary and knowledge of authors. Rho is positive 0.4, so there is a positive, but very weak relation between the two variables, and since, our result is insignificant we cannot be sure that if we drew another random sample from the population that we got the same result.

Modellos
```{r}
ggplot(Final, aes(acc_voc_percent, acc_forf_percent)) + 
  geom_point()

mod <- lm(acc_voc_percent ~ acc_forf_percent, data = Final)
coef(mod)


accuracy_mixed <- lmer(acc_voc_percent ~ Alder + (1 | Fakultet), data = Final)
summary(accuracy_mixed)
confint(accuracy_mixed)

lmHeight2 <- lm(acc_voc_percent~acc_forf_percent + Bøger + Fakultet, data = Final) #Create a linear regression with two variables
summary(lmHeight2) #Review the results -se screen shot i bachelor mappe
#https://www.datacamp.com/tutorial/linear-regression-R

    #Mat model PDF
# a <- rep(0,95) 
# for (i in 1:95){
#   lmerlmer <- lm(acc_voc_percent ~ acc_forf_percent + Bøger + Alder  + Køn  ,
#                        data = complete(Final , i))
#   
#   lmer2 <- lm(acc_voc_percent ~ acc_forf_percent + Bøger + Alder * Køn ,
#                          data = complete(Final , i))
# a[i] <- anova(lmer2, lmerlmer , test = "LRT")[2,5]
# }
# Sign_tests1 <- sum(ifelse(a < 0.05 , 1 , 0))
# p_value1 <-sum(a)/95
# test1 <- c(Sign_tests1,p_value1)

# tjek for alder 
# own gender bias 
```
#MAT# model halløj fra aflevering
```{r}

#helt fucked output, når jeg adder bøger, alder mv...
model_fin <- lm(acc_voc_percent ~ acc_forf_percent + Køn, data = Final)


summary(model_fin)

```

correlater de? model, kan det predictes det ene by det andet?
Tjek om det er de samme forfattere alle kender og omvendt om alle misser de samme

#CLUSTER ANALYSIS#
```{r}
pairs(Final[6:11])

plot(Final$acc_voc_percent~ Final$acc_forf_percent, data = Final)
with(Final,text(Final$acc_voc_percent ~ Final$acc_forf_percent, labels=Final$ID,pos=4))
```

```{r}
#Normalization
z <- Final[,c(6:11)]
means <- apply(z,2,mean)
sds <- apply(z,2,sd)
nor <- scale(z,center=means,scale=sds)

#distance matrix 
distance = dist(nor)

#Hierarchical agglomerative clustering 
Final.hclust = hclust(distance)
plot(Final)
plot(Final.hclust,labels=Final$ID,main='Default from hclust')
plot(Final.hclust,hang=-1, labels=Final$ID,main='Default from hclust')

#Hierarchical agglomerative clustering using “average” linkage
Final.hclust<-hclust(distance,method="average") 
plot(Final.hclust,hang=-1) 

#Cluster membership
member = cutree(Final.hclust,2)
table(member)

#Characterizing clusters
aggregate(nor,list(member),mean)
aggregate(Final[,-c(1,1)],list(member),mean)

#Silhouette Plot
plot(silhouette(cutree(Final.hclust,2), distance))

#Scree plot
wss <- (nrow(nor)-1)*sum(apply(nor,2,var))
for (i in 1:2) wss[i] <- sum(kmeans(nor, centers=i)$withinss)
plot(1:2, wss, type="b", xlab="Number of Clusters", ylab="Within groups sum of squares")

#K-means clustering
set.seed(123)
kc<-kmeans(nor,2)
kc

ot<-nor
datadistshortset<-dist(ot,method = "euclidean")
hc1 <- hclust(datadistshortset, method = "complete" )
pamvshortset <- pam(datadistshortset,3, diss = FALSE)
clusplot(pamvshortset, shade = FALSE,labels=2,col.clus="blue",col.p="red",span=FALSE,main="Cluster Mapping",cex=1.2)

#scree plot for optimal number of clusters 
fviz_nbclust(nor, kmeans, method = "wss")

#plot
k2 <- kmeans(nor, centers = 2, nstart = 25) #nstart is the number of times k-means will be repeated to find the optimal number of clusters 
fviz_cluster(k2, choose.vars = c("acc_voc_percent", "acc_forf_percent") ,data = nor)


set.seed(11)
k23 <- kmeans(nor, centers = 2, nstart = 25)
sil <- silhouette(k23$cluster, dist(nor), ordered = FALSE)
row.names(sil) <- row.names(nor) # Needed to use label option
fviz_silhouette(sil, label = TRUE)

# We see that Missouri and Arkansas are the poorest fits within their assigned clusters. We might want to take this into consider when interpreting the results for those states.

```

```{r}
# The author of the factoextra package, Alboukadel Kassambara, informed me that if you omit the choose.vars argument, the function fviz_cluster transforms the initial set of variables into a new set of variables through principal component analysis (PCA). This dimensionality reduction algorithm operates on the four variables and outputs two new variables (Dim1 and Dim2) that represent the original variables, a projection or "shadow" of the original data set. Each dimension represent a certain amount of the variation (i.e. information) contained in the original data set. In this example, Dim1 and Dim2 represent 73% and 22.9% respectively. When plotted, this lower-dimensional picture can be difficult to interpret. In exploratory data analysis, it is therefore perhaps more useful to purposefully select two variables at a time through the choose.vars argument, and then compare the plots.
```

Correlation Matrix
```{r}
library(corrplot)
library(RColorBrewer)
M <-cor(Final[6:11])
corrplot(M, type="upper", order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))
```




